\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-24 document/XSGRB_sample.tex

>>>>

	\subsection{GRB130606A (z = 5.913)}
	The data presented here also formed the basis of GCN \#
	14816\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14816.gcn3}} and is published
	in \citet{Hartoog2015}.
	The observations consists of three 2x600sec visits starting 7.1 hr after the burst at fairly
	high airmass.
	We detect absorption features from a wide range of ions at z=5.913 
	as well as intervening absorption at $z=2.313, 2.521, 3.415, 4.6448, 4.6468, 4 and 4.6495$.

	\subsection{GRB151021A (z = 2.330)}
	The data presented here also formed the basis of GCN \#
	18426\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not published
	elsewhere.
	The observation was carried out in RRM starting 44 min af the GRB trigger.
	We detect absorption features from a wide range of ions at z=2.330 
	as well as intervening absorption at $z=1.49$.

	\subsection{GRB160203A (z = 3.517)}
	The data presented here also formed the basis of GCN \#
	18982\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/18982.gcn3}} and is not published
	elsewhere.
	The observation was carried out in RRM starting 18 min af the GRB trigger.
	We detect absorption features from a wide range of ions at z=3.517 
	as well as intervening absorption at $z=2.203$.
